A modelling strategy to improve cacao quality and productivity

### 2021-09-02 papers/model/paper_model.tex
equations

The SIMPLE model performance was evaluated by comparing simulated values cocoa yield with those reported by Fedecacao from cocoa plantations, using statistical indices of relative-RMSE (RRMSE) \citep{Zao2019simple} and coefficient of determination (R$^{2}$) \citep{Zao2019simple, Bai2020, Camargo2019aquacropr}. The harvest date predicted was supported by \textcolor{red}{Adriana results}
Yield reports from 20190 to 2020  were shared by Federación Nacional de Cacaoteros - Fedecacao.

\subsection{Outputs}

>>>>

The SIMPLE model performance was evaluated by comparing simulated values cocoa yield with those reported by Fedecacao from cocoa plantations, using statistical indices of relative-RMSE (RRMSE) (Equ. \ref{equ:RMSE}) \citep{Zao2019simple} and coefficient of determination (R$^{2}$) (Equ. \ref{equ:R2}) \citep{Zao2019simple, Bai2020, Camargo2019aquacropr}. The harvest date predicted was supported by \textcolor{red}{Adriana results}
Yield reports from 20190 to 2020  were shared by Federación Nacional de Cacaoteros - Fedecacao.

\begin{equation}
RMSE= \sqrt{\frac{1}{n}  \sum_{i=1}^{n} (Y_{i}-X_{i})^{2} } 
\label{equ:RMSE}
\end{equation}

\begin{equation}
R^{2}= 1- \frac{\sum_{i=1}^{n} (Y_{i}-X_{i})^{2}}{{\sum_{i=1}^{n}(Y_{i}-0)}^{2}}
\label{equ:R2}
\end{equation}
